Demes: a standard format for demographic models

### 2022-08-08 software-table.tex
added author and software for MSMC
fixed table error on software-table, added citation

>>>>

\MSMC & A script provided in the MSMC-tools repository (https://github.com/stschiff/msmc-tools)
    converts MSMC \citep{SchiffelsDurbin2014,WangSchiffels2020} output to the demes format. Instructions are available in the Guide (https://github.com/stschiff/msmc-tools/blob/master/msmc-tutorial/guide.md).\\
